---
output: github_document
---

## Edit stan models using R

This package facilitates editing of stan model code using R. This includes adding/removing blocks, extracting variable names, and inserting/removing lines.

Development of this package was inspired by the `<bi_model>` class in the [rbi](https://github.com/sbfnk/rbi) package.

## Installation

The development version can be installed using `pak`
```{r eval=FALSE}
pak::pak("epiforecasts/stanedit")
```

## Example

First we load a stan model and prepares it for editing using the functionality in this package.

```{r}
library("stanedit")
#' model_file_name <- system.file(package = "stanedit", "regression.stan")
#' reg <- stanedit(filename = model_file_name)
#' reg
```

Let's say we want to add standard normal priors for alpha and beta.
We can do this using

```{r}
insert_lines(reg,
  lines = c(
    "alpha ~ std_normal();",
    "beta ~ std_normal();"
  )
  after = 12
)
```

## Contributors


<!-- ALL-CONTRIBUTORS-LIST:START - Do not remove or modify this section -->
<!-- prettier-ignore-start -->
<!-- markdownlint-disable -->

All contributions to this project are gratefully acknowledged using the [`allcontributors` package](https://github.com/ropensci/allcontributors) following the [all-contributors](https://allcontributors.org) specification. Contributions of any kind are welcome!

### Code


<a href="https://github.com/epiforecasts/qrensemble/commits?author=sbfnk">sbfnk</a>, 
<a href="https://github.com/epiforecasts/qrensemble/commits?author=seabbs">seabbs</a>



### Issues


<a href="https://github.com/epiforecasts/qrensemble/issues?q=is%3Aissue+commenter%3Anikosbosse">nikosbosse</a>


<!-- markdownlint-enable -->
<!-- prettier-ignore-end -->
<!-- ALL-CONTRIBUTORS-LIST:END -->

# Document Title
